---
title: "Automation of ARK Data Collection and Analysis"
author: "Oscar Daniel"
date: '2022-03-29'
output: powerpoint_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
 
knitr::opts_chunk$set(warning = FALSE, message = FALSE) 

```

#### **Preamble**

Call libraries, set numbers not to display as exponents and import raw data

```{r preamble}
library(tidyverse)
library(dplyr)
library(lubridate)
library(ggplot2)
library(ggthemes)
library(knitr)
options(scipen = 999)
raw_data <- read.csv(file = "RAW_DATA\\Data Extract.csv")
Clean_Data <- raw_data 
```

## Data Tidying

Before data analysis can be done, the data needs to be changed so that it only has information that we want to look at, that the data is in the correct format and that there is no sensitive information contained within it.

#### **Anonymise NHS No.**

Full NHS numbers are included in our raw data so we want to anonymise this to prevent sensitive data being shared. Turning the NHS number into an arbitrary ID number is an easy way to do this whilst still retaining the grouping of data to an individual.

```{r anonymise}
#change NHS# into an arbitrary Patient ID No
PID <- Clean_Data %>%                                        # Create ID by group
  group_by(NHS.) %>%
  mutate(ID = cur_group_id())
Clean_Data$NHS. <- PID$ID
```

#### **Convert Data into Correct Format**

As the date columns come in character format, we need to convert them into date types so we can manipulate them properly later on. We can also set our character data to one case so that it is more readable and predictable.

```{r date format and rx length}
#make columns dates not characters
Clean_Data$Prescription.start <- dmy_hm(Clean_Data$Prescription.start) 
Clean_Data$Prescription.end <- dmy_hm(Clean_Data$Prescription.end)


#make all character columns same case to reduce number of duplicates and ease readability

Clean_Data$Reason.given <-str_to_upper(Clean_Data$Reason.given, locale ="en") 
Clean_Data$Name <-str_to_title(Clean_Data$Name, locale ="en")
Clean_Data$Route <-str_to_title(Clean_Data$Route, locale ="en")

#take the difference between the start and end times of each rx, then make that a new column
Clean_Data$Prescription_Length <- interval(Clean_Data$Prescription.start, Clean_Data$Prescription.end) / hours(1)
head(select(Clean_Data, c(NHS., Prescription_Length)))



```



#### **Remove inappropriate data**

First we need to format data remove any irrelevant or erroneous data.

```{r clean up}
#remove duplicates
Clean_Data <- Clean_Data[!duplicated(Clean_Data), ]

#remove prescriptions before Dec 1st 2021 and ending after 2022
 
Clean_Data <- filter(Clean_Data, Prescription.start >= as.POSIXct("2021-12-01 00:00"))

Clean_Data <- filter(Clean_Data, Prescription.end < as.POSIXct("2022-12-31 00:00"))


  
#remove any stat, bleed, prophylactic abx, leg cramps, hepatic encephalopathy, SIADH or nystatin rx
  Clean_Data <- Clean_Data %>%
    filter(!(grepl("*BLEED*", Reason.given) | grepl("*PROPHY*", Reason.given) | grepl("*CRAMP*", Reason.given) | 
               grepl("MS", Reason.given) | grepl("*ONCE*", Frequency) | grepl("H.ENCEPH*", Reason.given) | grepl("*HEPATIC ENCEPHALOPATHY*", Reason.given) | grepl("NYSTATIN", Name) | grepl("NYSTAN", Name) | grepl("SIADH", Reason.given) | grepl("^Amantadine", Name)))
  
#remove any prescriptions where they could not have had more than one dose 

 Clean_Data <- filter(Clean_Data, Frequency == "THREE times a DAY" & Prescription_Length > 8 | Frequency == "FOUR times a DAY" & Clean_Data$Prescription_Length > 6 | Frequency == "TWICE a DAY" & Prescription_Length > 12)

```

#### **Regular expressions**

Use some regex to normalise common indication names, remove ambiguous abbreviations and correct for some spelling mistakes

```{r regex}
#make all UTIs display as Urinary Tract Infection
  Clean_Data$Reason.given <- gsub( "UTI", "URINARY TRACT INFECTION",Clean_Data$Reason.given) 
  
  #make all community acquired pneumonia display as CAP
  Clean_Data$Reason.given <- gsub("CAP", "COMMUNITY ACQUIRED PNEUMONIA", Clean_Data$Reason.given)
  
  #make all IEoCOPD as IECOPD
  Clean_Data$Reason.given <- gsub("IECOPD", "INFECTIVE EXACERBATION OF CHRONIC OBSTRUCTIVE PULMONARY DISEASE", Clean_Data$Reason.given) 
  
  #make all LRTI full name
  Clean_Data$Reason.given <- gsub("LRTI", "LOWER RESPIRATORY TRACT INFECTION", Clean_Data$Reason.given) 
  #make any blank indications "Unrecorded"
  Clean_Data$Reason.given <- sub("^$", "UNRECORDED", Clean_Data$Reason.given)
  
  #correct common spelling mistakes
  Clean_Data$Reason.given <- gsub("PYONEPHRITIS", "PYELONEPHRITIS", Clean_Data$Reason.given)
  
  Clean_Data$Reason.given <- replace(Clean_Data$Reason.given,grep("DIFF",Clean_Data$Reason.given),"CLOSTRIDIUM DIFFICILE")
    
  
  Clean_Data$Reason.given <- str_to_title(Clean_Data$Reason.given)
  head( select(Clean_Data, c(NHS.,Name, Reason.given)))
```

## Data Wrangling

This is where we start to manipulate and extract important information from our dataset to be used in our visualisations.

#### Find Pertinent Information



To help us understand what data is in each column we can look at the distinct values in each. This is much faster than looking through and making a note of what we see. For the indication this is useful to see if there are any common ways that things are misspelled;

```{r distinct example}
indications <- distinct(Clean_Data ,Clean_Data$Reason.given) %>% 
  head()
```

This can further inform our tidying process and clean up more commonly misspelled words and phrases.

#### **Pivoting**

Now that we have our data fairly tidy and we have the necessary information added, we want to arrange the data in a way which will reflect the way the ark project wants the data to look;

```{r pivoting}

#pivot wide
abx_per_indication <- Clean_Data %>% arrange(Prescription.start) %>%  group_by(NHS.) %>% 
  group_by(NHS., Reason.given) %>% 
  mutate(rn = row_number()) %>%
  pivot_wider(values_from = c(Name,Route,Prescription.start,Prescription.end, Dose, 
                              Frequency, ARK.category, Prescription_Length ),
              names_from =  rn)
```

This groups the data by person and by the indication (as in ARK antibiotics should only be grouped by the same indication), and makes each row a course of antibiotics for an illness, rather than single prescriptions.

Now that our data is better presented we can look for certain things.

For example we may want to find the most commonly prescribed antibiotics, or the most common reasons that antibiotics are prescribed;


#### Find popular antibiotics and popular indications over time

```{r find intermediate values}

#find top n most frequently prescribed abx
pop_abx <- Clean_Data %>%
  count(Name) %>%
  top_n(10) %>% 
  arrange(-n) %>% 
  head()

#get the agents lined up by their start times and find their frequency on that day
agent_by_date <- Clean_Data %>%
  group_by(Prescription.start) %>%
  count(Name) 
#then find their cumulative frequency over time
agent_by_date <- agent_by_date %>%
  group_by(Name) %>%
  mutate(Cum_n = cumsum(n)) 



#find top n most frequent indications
pop_indic <- abx_per_indication %>% 
  group_by(Reason.given) %>%
  count(Reason.given) %>% 
  arrange(-n) 
pop_indic <- head(pop_indic, n = 10)

#then select only the most commonly prescribed abx
pop_agent_by_date <- filter(agent_by_date, Name %in% pop_abx$Name)
  

agent_by_reason <- Clean_Data %>%
  group_by(Reason.given) %>%
  count(Name)

agent_by_reason <- filter(agent_by_reason,Reason.given %in% pop_indic$Reason.given) %>%
  print()
#organise pop indic by date and count how many over time
indic_by_date <- Clean_Data %>% 
  group_by(Prescription.start) %>% 
  count(Reason.given)
#find most common indications
indic_by_date <- indic_by_date %>% 
  filter(Reason.given %in% pop_indic$Reason.given) 
#find totals over time  
indic_by_date <- indic_by_date  %>% 
  mutate(Reason.given = str_to_title(Reason.given)) %>% 
  group_by(Reason.given) %>% 
  mutate(cum_n = cumsum(n))
```

#### **Record Decisions**

As ARK wants us to record the decisions that were made between each prescription, such as IV to Oral, Oral to IV or stopped.


To speed up processing time during testing just take a sample of x number patients

```{r}
abx_per_indication = abx_per_indication[sample(1:nrow(abx_per_indication),100),]
```

```{r Interval Calculation}
abx_per_indication <- abx_per_indication %>% 
  mutate(interval_1 = interval(Prescription.start_1, Prescription.start_2) / hours (1),
         interval_2 = interval(Prescription.start_2, Prescription.start_3) / hours (1),
         interval_3 = interval(Prescription.start_3, Prescription.start_4) / hours (1),
         interval_4 = interval(Prescription.start_4, Prescription.start_5) / hours (1),
         interval_5 = interval(Prescription.start_5, Prescription.start_6) / hours (1),
  )


```

```{r remove na cols}
remove_all_na <- function(data){
 data <- data[ , colSums(is.na(data)) < nrow(data)]
  return(data)
  
}
```


```{r decision tree}


#try it by a decision tree
node0 <- abx_per_indication %>% ungroup()
#was there only one prescription?
node1a <- node0 %>%  #single rx course
  filter(is.na(Name_2)) %>% remove_all_na()

node1b <- abx_per_indication %>% #multiple rx course
  filter(!is.na(Name_2)) %>% remove_all_na()

#if there was only one prescription was it prescribed for less than 72hours?
  node2a <- node1a %>% 
    filter(Prescription_Length_1 <= 72) #single rx course, <72hr
  
  node2b <- node1a %>% 
    filter(Prescription_Length_1 > 72) %>% remove_all_na()#single rx course, >72hr

  
nrow(node2a)/ (nrow(node2a)+nrow(node2b))*100 #% of single rx which were stopped within 72hrs
  
  
  #was the initial rx a double rx (started less than one hour from each other)
  node2c <- node1b %>% #double rx
    filter(interval(Prescription.start_1,Prescription.start_2)/hours(1) <= 1) %>% #
    remove_all_na()
  
  node2d <- node1b %>% #single initial rx
    filter(!interval(Prescription.start_1,Prescription.start_2)/hours(1) <= 1) %>% 
    remove_all_na()

nrow(node2c)/ (nrow(node2c)+nrow(node2d))*100  #%of rx courses >=2 that were double rx
  
{      #if not double rx,was the first rx IV?
      node3a <- node2d %>% 
        filter(Route_1 == "Intravenous") %>% #single initial rx which was IV
        remove_all_na()
      
      node3b <- node2d %>% 
        filter(!Route_1 == "Intravenous") %>% #single initial rx which was oral
        remove_all_na()
      
nrow(node3a)/ (nrow(node3a)+nrow(node3b))*100 #% of rx courses >=2 that had the first prescription as single IV


      #if double rx then was total course length >=3?
      node3c <- node2c %>% 
        filter(!is.na(Name_3)) #double rx which had more than 3 rx in the course
      
      node3d <- node2c %>% 
        filter(is.na(Name_3)) #double rx which only had the initial double 
      
      #if there was one rx and it was rx for less than 72 hours, was it IV?
      node3e <- node2a %>% 
        filter(Route_1 == "Intravenous") #single rx, short, IV - outcome stopped within 72 hrs
      leaf1 <- node3e %>% mutate(decision = "Stopped <72")
      node3f <- node2a %>% 
        filter(!Route_1 == "Intravenous")    #single rx, short, oral - outcome stopped within 72hrs
      leaf2 <- node3d %>% mutate(decision = "Stopped <72")
      #if there was one rx and it was longer than 72 hrs wa it IV?
      node3g <- node2b %>% 
        filter(Route_1 == "Intravenous") %>%  remove_all_na() #single rx, long, IV - outcome not changed or stopped within 72hrs
      leaf3 <- node3g %>% mutate(decision = "Not Reviewed")
      node3h <- node2b %>% 
        filter(!Route_1 == "Intravenous") %>%  remove_all_na() #single rx, long, oral - outcome not changed or stopped within 72hrs
      leaf4 <- node3h %>% mutate(decision = "Not Reviewed")
      }
        #if double rx with more than 3, were both initial drugs the same route?
        
      {  node4a <- node3c %>% 
          filter(Route_1 == Route_2) #double rx, course >=3, same initial route 
        node4b <- node3c %>% 
          filter(!Route_1 == Route_2) #double rx, course >=3, mixed route
        
        #if double rx with less than 3, were both initial drugs same route?
        node4c <- node3d %>% 
          filter(Route_1 == Route_2) #double rx, course <3, same initial route 
        node4d <- node3d %>% 
          filter(!Route_1 == Route_2) #double rx, course <3, mixed route
       #if single initial rx, course > 1, was the first prescription stopped within 72 hours? 
         node4e <- node3a %>% 
          filter(Prescription_Length_1 <=72) #single initial rx, course >1, IV, reviewed <72
         node4f <- node3a %>% 
          filter(Prescription_Length_1 >72) #single initial rx, course >1, IV, reviewed >72
         node4g <- node3b %>% 
          filter(Prescription_Length_1 <=72) #single initial rx, course >1, oral, reviewed <72
         node4h <- node3b %>% 
          filter(Prescription_Length_1 >72) #single initial rx, course >1, oral, reviewed >72
          
        }
        
        # if same route, was it IV (double rx >= 3 in course)
 {         node5a <- node4a %>% 
            filter(Route_1 == "Intravenous") #double rx, course >=3, both IV
          node5b <- node4a %>% 
            filter(!Route_1 == "Intravenous") #double rx, course >=3, both oral
 }   
      {  #if not same route, were either stopped before 72 hours (double rx >= 3 in course, different routes)
          node5c <- node4b %>% 
            filter(Prescription_Length_1 <=72 | Prescription_Length_2 <= 72) # double rx, course >3, different routes, either was stopped <72
          node5d <- node4b %>% 
            filter(!(Prescription_Length_1 <=72 | Prescription_Length_2 <= 72)) #double rx, course >3, different routes, neither was stopped <72
        #if same route, was it IV (double rx less than 3 in course)
          node5e <- node4c %>% 
            filter(Route_1 == "Intravenous") #double rx, <3 course, both IV
          node5f <- node4c %>% 
            filter(!Route_1 == "Intravenous") #double rx, <3 course, both oral
      }     
      {  #if not same route, were either stopped before 72 hours (double rx <3 in course, different routes)
          node5g <- node4d %>% 
            filter(Prescription_Length_1 <=72 | Prescription_Length_2 <= 72) %>% 
            remove_all_na() # double rx, course <3, mixed routes, either was stopped <72
          
          node5h <- node4d %>% 
            filter(!(Prescription_Length_1 <=72 | Prescription_Length_2 <= 72)) %>% 
            remove_all_na() # double rx, course <3, mixed routes, neither stopped <72
         
          
           #single initial IV, course >1, reviewed < 72 hrs, next rx same? (i.e same route, drug, dose and frequency) 
          node5i <- node4e %>% 
            filter(Route_1 == Route_2 & Name_1 == Name_2 & Dose_1 == Dose_2 & Frequency_1 == Frequency_2) #initial IV, course >1, rev < 72, rx kept same
          leaf5 <- node5i %>% remove_all_na() %>% mutate(decision = "No change")                                                                                 #this will allow for reviews after 6 hrs to count,
                                                                                                          #should it be a minimum of  day? A decision has still been made 
                                                                                                          #also what is the upper limit - is it exactly 72 hrs?
          
          node5j <- node4e %>% 
            filter(!(Route_1 == Route_2 & Name_1 == Name_2 & Dose_1 == Dose_2 & Frequency_1 == Frequency_2)) #initial IV, course >1, rev < 72, rx changed
          
           #single initial IV, course >1, reviewed > 72 hrs, next rx same? (i.e same route, drug, dose and frequency) 
          node5k <- node4f %>% 
            filter(Route_1 == Route_2 & Name_1 == Name_2 & Dose_1 == Dose_2 & Frequency_1 == Frequency_2) #initial IV, course >1, rev > 72, rx kept same
          leaf6 <- node5k %>% mutate(decision = "No change >72")                                                                                             
          
          node5l <- node4f %>% 
            filter(!(Route_1 == Route_2 & Name_1 == Name_2 & Dose_1 == Dose_2 & Frequency_1 == Frequency_2)) #initial IV, course >1, rev > 72, rx changed
                   
           #single initial oral, course >1, reviewed < 72 hrs, next rx same? (i.e same route, drug, dose and frequency) 
          node5m <- node4g %>% 
            filter(Route_1 == Route_2 & Name_1 == Name_2 & Dose_1 == Dose_2 & Frequency_1 == Frequency_2) #initial oral, course >1, rev < 72, rx kept same
                        # **LEAF**
                                                                                                          
          
          node5n <- node4g %>% 
            filter(!(Route_1 == Route_2 & Name_1 == Name_2 & Dose_1 == Dose_2 & Frequency_1 == Frequency_2)) #initial oral, course >1, rev < 72, rx changed
          
           #single initial oral, course >1, reviewed > 72 hrs, next rx same? (i.e same route, drug, dose and frequency) 
          node5o <- node4h %>% 
            filter(Route_1 == Route_2 & Name_1 == Name_2 & Dose_1 == Dose_2 & Frequency_1 == Frequency_2) #initial oral, course >1, rev > 72, rx kept same
                                # **LEAF**
                                                                                                           
          
          node5p <- node4h %>% 
            filter(!(Route_1 == Route_2 & Name_1 == Name_2 & Dose_1 == Dose_2 & Frequency_1 == Frequency_2)) #initial oral, course >1, rev > 72, rx changed
          
          }
          
          
{         
  
          # if not same route, course >=3, and either stopped before 72 hours, were they both stopped at the same time? i.e within 6 hours of each other  
          #(double rx more than 3 in course, different routes)
          #careful that interval can be +ve or -ve so need to use between() function
            node6a <- node5c %>% 
              filter(between(interval(Prescription.end_1, Prescription.end_2)/hours(1),-6,6)) #double rx, course >=3, mixed route, either stopped <72
                                                                                                        #stopped at same time
            node6b <- node5c %>% 
              filter(!between(interval(Prescription.end_1, Prescription.end_2)/hours(1),-6,6))#double rx, course >=3, mixed route, either stopped <72
                                                                                                        #stopped separately
              
             #if same route, were either stopped before 72 hours (double rx < 3 in course, both IV)
            node6c <- node5e %>% 
              filter(Prescription_Length_1 <=72 | Prescription_Length_2 <= 72) #double rx, course <3, both IV, either stopped before 72hrs 
            node6d <- node5e %>% 
              filter(!(Prescription_Length_1 <=72 | Prescription_Length_2 <= 72)) #double rx, course <3, both IV, neither stopped before 72hrs            
    
            # if mixed route, course <3, and either stopped before 72 hours, were they both stopped at the same time? i.e within 6 hours of each other  
          #(double rx more than 3 in course, different routes)
            node6e <- node5g %>% 
              filter(between(interval(Prescription.end_1, Prescription.end_2)/hours(1),-6,6)) #double rx, course <3, mixed route, either stopped <72
                                                                                                        #stopped at same time - outcome; reviewed <72 hrs and both stopped
                                                                                                        # **LEAF**
            node6f <- node5g %>% 
              filter(!between(interval(Prescription.end_1, Prescription.end_2)/hours(1),-6,6)) #double rx, course <3, mixed route, either stopped <72
                                                                                                        #stopped separately
            node6g <- node5a %>% 
               filter(Prescription_Length_1 <=72 | Prescription_Length_2 <= 72) ##double rx, course >=3, both IV, either stopped <72
            
}           
     {      node6h <- node5a %>% 
              filter(!(Prescription_Length_1 <=72 | Prescription_Length_2 <= 72)) ##double rx, course >=3, both IV, neither stopped <72
                      
            node6i <- node5b %>% 
               filter(Prescription_Length_1 <=72 | Prescription_Length_2 <= 72) ##double rx, course >=3, both oral, either stopped <72
            
            
            node6j <- node5b %>% 
              filter(!(Prescription_Length_1 <=72 | Prescription_Length_2 <= 72)) ##double rx, course >=3, both oral, neither stopped <72
            

          
          node6k <- node5d %>%
            filter(between(interval(Prescription.end_1, Prescription.end_2)/hours(1),-6,6)) #double rx, course >=3, mixed route, neither stopped <72
                                                                                                        #stopped at same time
            node6l <- node5d %>% 
              filter(!between(interval(Prescription.end_1, Prescription.end_2)/hours(1),-6,6))#double rx, course >=3, mixed route, neither stopped <72
                                                                                                        #stopped separately
            node6m <- node5f %>%
               filter(Prescription_Length_1 <=72 | Prescription_Length_2 <= 72) #double rx, course <3, both oral, either stopped before 72hrs 
            node6n <- node5f %>% 
              filter(!(Prescription_Length_1 <=72 | Prescription_Length_2 <= 72)) #double rx, course <3, both oral, neither stopped before 72hrs
 
            node6o <- node5h %>% 
              filter(between(interval(Prescription.end_1, Prescription.end_2)/hours(1),-6,6)) #double rx, course <3, mixed routes, neither stopped <72
                                                                                              #stopped together
            node6p <- node5h %>% 
              filter(!between(interval(Prescription.end_1, Prescription.end_2)/hours(1),-6,6))  
                                                    #double rx, course <3, mixed routes, neither stopped <72
                                                    #not stopped together
            node6q <- node5j %>% #initial IV, course >1, rev < 72, rx changed, was it switched to oral? **LEAF**
              filter(Route_2 == "Oral") #initial IV, course >1, rev < 72, rx changed, switched to oral
            
            node6r <- node5j %>% 
              filter(!Route_2 == "Oral") #initial IV, course >1, rev < 72, rx changed, not switched to oral
            
            node6s <- node5l %>%  #initial IV, course >1, rev > 72, rx changed
              filter(Route_2 == "Oral") #changed to oral>72hrs      ***LEAF**
           
             node6t <- node5l %>% 
              filter(!Route_2 == "Oral")#not changed to oral
            
             node6u <- node5n %>%  #initial oral, course >1, rev < 72, rx changed
               filter(Route_2 == "IV") #changed to IV **LEAF**
             
             node6v <- node5n %>%  #initial oral, course >1, rev < 72, rx changed
               filter(!Route_2 == "IV") #not changed to IV
             
             node6w <- node5p %>% #initial oral, course >1, rev > 72, rx changed
               filter(Route_2 == "IV") #changed to IV **LEAF**
               
             node6x <- node5p %>% #initial oral, course >1, rev > 72, rx changed
               filter(!Route_2 == "IV") #not changed to IV
             }
  {            node7a <- node6a %>% #double rx, course >=3, mixed route, either stopped <72, stopped at same time
                filter(!is.na(Route_4) ) #more than one more rx
              node7b <- node6a %>% 
                filter(is.na(Route_4)) #not more than one more rx
              
              
            #if not same route, and either were stopped before 72 but not stopped at the same time, was the IV stopped first?  (double rx more than 3 in course)
              node7c <- node6b %>% 
                filter(Route_1 == "Intravenous" & Prescription.end_1 < Prescription.end_2 | Route_2 == "Intravenous" & Prescription.end_2<Prescription.end_1) %>% 
                   remove_all_na() #double rx, course >=3, mixed route, either stopped <72, stopped separately, IV stopped first
              node7d <- node6b %>% 
                filter(!(Route_1 == "Intravenous" & Prescription.end_1 < Prescription.end_2 | Route_2 == "Intravenous" & Prescription.end_2<Prescription.end_1)) %>%
                    remove_all_na() #double rx, course >=3, mixed route, either stopped <72, stopped separately, oral stopped first
              
                             # if same route, course <3, and either stopped before 72 hours, were they both stopped at the same time? i.e within 6 hours of each other
              node7e <- node6c %>% 
                filter(between(interval(Prescription.end_1, Prescription.end_2)/hours(1),-6,6)) %>% 
                  remove_all_na() #double rx, course <3, both IV, either stopped before 72hrs 
                                                                                                  #stopped together- outcome; reviewed <72hrs and both stopped
              
              node7f <- node6c %>%              
                filter(!between(interval(Prescription.end_1, Prescription.end_2)/hours(1),-6,6))%>% 
                  remove_all_na() #double rx, course <3, both IV, either stopped before 72hrs
                                                                                                          #stopped separately  
                
                # if same route, course <3, and either stopped before 72 hours, were they both stopped at the same time? i.e within 6 hours of each other
              node7g <- node6d %>% 
                filter(between(interval(Prescription.end_1, Prescription.end_2)/hours(1),-6,6)) %>% 
                  remove_all_na() #double rx, course <3, both IV, neither stopped before 72hrs 
                                                                                                  #stopped together- outcome; reviewed <72hrs and both stopped
              
              node7h <- node6d %>%              
                filter(!between(interval(Prescription.end_1, Prescription.end_2)/hours(1),-6,6))%>% 
                  remove_all_na() #double rx, course <3, both IV, neither stopped before 72hrs
                                                                                                          #stopped separately 
              
              
                          #mixed route, and either were stopped before 72 but not stopped at the same time, was the IV stopped first?  (double rx more < 3 in course)
  }
              
{              
              #double rx, course <3, mixed route, either stopped <72, stopped separately, was the IV stopped first?
              node7g <- node6f %>% 
                filter(Route_1 == "Intravenous" & Prescription.end_1 < Prescription.end_2 | Route_2 == "Intravenous" & Prescription.end_2<Prescription.end_1) %>% 
                remove_all_na() #double rx, course <3, mixed route, either stopped <72, stopped separately, IV stopped first
              node7h <- node6f %>% 
                filter(!(Route_1 == "Intravenous" & Prescription.end_1 < Prescription.end_2 | Route_2 == "Intravenous" & Prescription.end_2<Prescription.end_1)) %>% 
                remove_all_na() #double rx, course <3, mixed route, either stopped <72, stopped separately, oral stopped first
              
              #double rx, course >=3, both IV, either stopped <72, stopped together?
              node7i <- node6g %>% 
                filter(between(interval(Prescription.end_1, Prescription.end_2)/hours(1),-6,6)) #double rx, course >=3, both IV, either stopped <72, stopped together
              
              node7j <- node6g %>% 
                 filter(!between(interval(Prescription.end_1, Prescription.end_2)/hours(1),-6,6)) #double rx, course >=3, both IV, either stopped <72, not stopped together
          
              }
                node8a <- node7a %>% #double rx, course >=3, mixed route, either stopped <72, stopped at same time, more than one more rx, #were the next two rx the same as the first two
                        #next two the same **LEAF**
                  filter((Route_1 == Route_3 & Name_1 == Name_3 & Dose_1 == Dose_3 & Frequency_1 == Frequency_3 & 
                            Route_2 == Route_4 & Name_2 == Name_4 & Dose_2 == Dose_4 & Frequency_2 == Frequency_4) | 
                           (Route_2 == Route_3 & Name_2 == Name_3 & Dose_2 == Dose_3 & Frequency_2 == Frequency_3 & 
                              Route_1 == Route_4 & Name_1 == Name_4 & Dose_1 == Dose_4 & Frequency_1 == Frequency_4)) 
                
                node8b <- node7a %>% 
                  #next two not both same
                   filter(!((Route_1 == Route_3 & Name_1 == Name_3 & Dose_1 == Dose_3 & Frequency_1 == Frequency_3 &
                             Route_2 == Route_4 & Name_2 == Name_4 & Dose_2 == Dose_4 & Frequency_2 == Frequency_4) |
                            (Route_2 == Route_3 & Name_2 == Name_3 & Dose_2 == Dose_3 & Frequency_2 == Frequency_3 & 
                               Route_1 == Route_4 & Name_1 == Name_4 & Dose_1 == Dose_4 & Frequency_1 == Frequency_4)))
                
                node8c <- node7b %>% #double rx, course >=3, mixed route, either stopped <72, stopped at same time, not more than one more rx
                                     #was the final rx the same as either of the first?
                  filter(((Route_1 == Route_3 & Name_1 == Name_3 & Dose_1 == Dose_3 & Frequency_1 == Frequency_3)| #final rx same as one of the first
                           (Route_2 == Route_3 & Name_2 == Name_3 & Dose_2 == Dose_3 & Frequency_2 == Frequency_3))) 
                
                node8d <- node7b %>% 
                   filter(!((Route_1 == Route_3 & Name_1 == Name_3 & Dose_1 == Dose_3 & Frequency_1 == Frequency_3)| #final rx not same as one of the first
                           (Route_2 == Route_3 & Name_2 == Name_3 & Dose_2 == Dose_3 & Frequency_2 == Frequency_3)))
```

```{r leaves}
leaf5 <- node5i %>% remove_all_na() %>% mutate(decision = "No change") 
```


```{r Decision 1}

#classify each change as per ARK protocol

#firstly, what was actually commenced
abx_per_indication <- abx_per_indication %>% 
  mutate(Decision_1 = case_when(
    Route_1 == "Intravenous" & Route_2 == "Intravenous" & interval_1 < 12 & 
      Prescription_Length_1 > 12 ~ 'Dual IV therapy started',
    Route_1 == "Intravenous" &  Route_2 == "Oral" & interval_1 < 12 & 
      Prescription_Length_1 > 12 ~ 'IV and Oral started',
    Route_1 =="Oral" & Route_2 == "Intravenous" & interval_1 < 12 ~ "IV and Oral started",
    Route_1 == "Intravenous" & Route_2 == "Oral" & interval_1 < 12 & 
      Prescription_Length_1 > 12 ~ 'Dual Oral therapy started',
    interval_1 > 12 | is.na(interval_1) | Prescription_Length_1 <=12 ~ paste0(Route_1, " started"),
    

                                TRUE ~ 'something else'
  ))
```

```{ deprecated}
test <- filter(abx_per_indication, NHS. ==  121)

#what happened after the initial prescription

abx_per_indication <- abx_per_indication %>% 
  mutate(Decision_2 = case_when(Route_1 == Route_2 & Name_1 == Name_2 & Dose_1 == Dose_2 & Frequency_1 == Frequency_2  ~ paste0(Route_2, " ", Name_2, " continued"),    
        Route_1 == Route_2 & Name_1 != Name_2 & Decision_1 == "Oral started"  ~ paste0('Agent switched to ', Name_2),
        Route_1 == Route_2 & Name_1 != Name_2 & Decision_1 == "Intravenous started" ~ paste0('Agent switched to ', Name_2),
        Route_1 == Route_2 & Dose_1 != Dose_2 & Frequency_1 != Frequency_2 & Name_1 == Name_2 ~ paste0('Regiment changed to ', Dose_2, " ",Frequency_2),
        
        Route_1 =="Intravenous" & Route_2 == "Intravenous" & ARK.category_2 == "FINAL" ~ paste0('Finalised as IV ', Name_2),
        Route_1 =="Oral" & Route_2 == "Oral" & is.na(Route_3) & ARK.category_2 == "FINAL" ~ paste0('Finalised as Oral ', Name_2),
        #see if there was a single agent switch
        Prescription.end_1 < Prescription.start_2 + 1 & Decision_1 != "IV and Oral started"  ~ paste0(Route_1, " to ", Route_2, " switch"),
        Prescription.end_1 < Prescription.start_2 + 1 & Decision_1 != "Dual IV therapy started"  ~ paste0(Route_1, " to ", Route_2, " switch"),
        Prescription.end_1 > Prescription.start_2 + 1 & Decision_1 != "IV and Oral started" ~ paste0(Route_2, " " ,Name_2, " added"),
        Prescription.end_1 > Prescription.start_2 + 1 & Decision_1 != "Dual IV therapy started" ~ paste0(Route_2, " " ,Name_2, " added"),
     is.na(Route_2)  & Prescription_Length_1 <=72 ~ paste0('Stopped as ', Route_1, ' within 72 hours'),
     is.na(Route_2) & Prescription_Length_1 > 72 ~ paste0('Stopped as ', Route_1, ' beyond 72 hours'),
     TRUE ~ "something else",))
     #Decision_1 == "IV and Oral started" # then becomes what decision three would look AT
        
        #Route_1 == Route_2 & Name_1 == Name_2 & Dose_1 == Dose_2 & Frequency_1 == Frequency_2  ~ 'No Change'
```  

```{ deprecated}
 abx_per_indication <- abx_per_indication %>% 
  mutate(Decision_2 = case_when(Prescription.end_1 < Prescription.start_3 +1 & Prescription.end_2 < Prescription.start_3 +1 & Decision_1 == "IV and Oral started" & Name_3 != NA  ~ paste0( "IV and Oral to ", Route_3, " switch"),
        Prescription.end_1 < Prescription.start_3 & Prescription.end_2 < Prescription.start_3 & Decision_1 == "Dual IV therapy started"  ~ paste0(Route_1, " to ", Route_3, " switch"),))
```
        

```{r Decision 2}
 abx_per_indication <- abx_per_indication %>% 
  mutate(Decision_2 = case_when(
    #if two agents were started at once, see if one of them was stopped and what replaced it
    Decision_1 == "IV and Oral started" & Prescription.end_1 < Prescription.start_3 + 10  & Prescription.start_4 > Prescription.start_3 + 10 ~ paste0(Name_1," ", Route_1  , " to ", Route_3 ," ", Name_3, " partial switch"),
                  Decision_1 == "IV and Oral started" & Prescription.end_2 < Prescription.start_3 + 10  & Prescription.start_4 > Prescription.start_3 + 10 ~ paste0(Name_2," ", Route_2  , " to ", Route_3 ," ", Name_3, " partial switch"),                                
                                
         Decision_1 == "Dual IV therapy started"  & Prescription.end_1 < Prescription.start_3 + 10 & Prescription.start_4 > Prescription.start_3 + 10 ~ paste0(Name_1," ", Route_1  , " to ", Route_3 ," ", Name_3, " partial switch"),
         Decision_1 == "Dual IV therapy started" & Prescription.end_2 < Prescription.start_3 + 10  & Prescription.start_4 > Prescription.start_3 + 10 ~ paste0(Name_1," ", Route_1  , " to ", Route_3 ," ", Name_3, " partial switch"),
    #what if one was stopped and nothing replaced it
    Decision_1 == "IV and Oral started" & Prescription.end_2 < Prescription.end_1 + 6  & is.na(Name_3) ~ paste0(Name_2," ", Route_2  , " stopped"),
    Decision_1 == "IV and Oral started" & Prescription.end_1 < Prescription.end_2 + 6  & is.na(Name_3) ~ paste0(Name_1," ", Route_1  , " stopped"),
    
    #see if both agents were stopped and what replaced them 
    
         Decision_1 == "IV and Oral started" & Prescription.end_1 < Prescription.start_3 + 10 & Prescription.end_2 < Prescription.start_3 + 10  & Prescription.start_4 > Prescription.start_3 + 10 ~ paste0(Route_2," and ", Route_1  , " to ", Route_3 ," ", Name_3, " total switch"),
    Decision_1 == "Dual IV therapy started" & Prescription.end_1 < Prescription.start_3 + 10 & Prescription.end_2 < Prescription.start_3 + 10  & Prescription.start_4 > Prescription.start_3 + 10 ~ paste0(Route_2," and ", Route_1  , " to ", Route_3 ," ", Name_3, " total switch"),
    #if both were stopped and that was the end of the course
  Decision_1 == "IV and Oral started" & is.na(Name_3) & between(interval(Prescription.end_1, Prescription.end_2) / hours(1), -1, 1 ) & Prescription_Length_1 <= 72  |
    Decision_1 == "Dual IV therapy started" & is.na(Name_3) & between(interval(Prescription.end_1, Prescription.end_2) / hours(1), -1, 1 )  & Prescription_Length_1 <= 72 ~  paste0("Both stopped within 72 hours"),
    Decision_1 == "IV and Oral started" & is.na(Name_3) & between(interval(Prescription.end_1, Prescription.end_2) / hours(1), -1, 1 ) & Prescription_Length_1 <= 72  |
    Decision_1 == "Dual IV therapy started" & is.na(Name_3) & between(interval(Prescription.end_1, Prescription.end_2) / hours(1), -1, 1 )  & Prescription_Length_1 > 72 ~  paste0("Both stopped beyond 72 hours"),
  #what if just one agent was initially prescribed and just re-prescribed exactly as it was
Decision_1 != "IV and Oral started" & Decision_1 != "Dual IV therapy started" & Decision_1 != "Dual Oral therapy started" &
  Name_1 == Name_2 & Route_1 == Route_2 & Dose_1 == Dose_2 & Frequency_1 == Frequency_2 ~ paste0("Prescription continued, reviewed after ",interval_1, " hours"),
  #what if just one agent was initially prescribed, and then was changed
  Decision_1 != "IV and Oral started" & Decision_1 != "Dual IV therapy started" & Prescription.end_1 < Prescription.start_2 +1 & Name_1 != Name_2 & Route_1 != Route_2 &  Dose_1 != Dose_2 & Frequency_1 != Frequency_2 ~ paste0(Name_1, " ", Route_1, " to ",Route_2, " ", Name_2, " switch" ),
  
  #what if something was added, before the first one was stopped?
   Decision_1 != "IV and Oral started" & Decision_1 != "Dual IV therapy started" & Decision_1 != "Dual Oral therapy started" & Prescription.start_2 < Prescription.end_1 +1 & is.na(Name_3) | 
      Decision_1 != "IV and Oral started" & Decision_1 != "Dual IV therapy started" & Prescription.start_2 < Prescription.end_1 +1 & Prescription.end_2 < Prescription.start_3 +10
    ~ paste0(Name_2, " ", Route_2, " added"),
  
        #between value between(value, lower limit, upper limit)
    
    #if only one agent was given
    is.na(Name_2) & Prescription_Length_1 <= 72 ~ paste0("Stopped as ", Route_1, " within 72 hours"),
    is.na(Name_2) & Prescription_Length_1 > 72 ~ paste0("Stopped as ", Route_1, " beyond 72 hours"),
      
    
    
         ))
    
    
  #  Route_2 =="Intravenous" & Route_3 =="Oral" ~ 'IV to Oral Switch',
   #                             Route_2 =="Oral" & Route_3 =="Intravenous"  ~ 'Oral to IV Switch',
    #                            Route_2 =="Intravenous" & Route_3 == "Intravenous" & is.na(Route_4)  ~ 'Finalised as IV',
     #                           Route_2 =="Intravenous" & is.na(Route_3) & Prescription_Length_2 <=72 ~ 'Stopped as IV within 72 hours',
      #                          Route_2 =="Oral" & is.na(Route_3)  & Prescription_Length_2 <=72 ~ 'Stopped as Oral within 72 hours',
       #                         Route_2 =="Intravenous" & is.na(Route_3) & Prescription_Length_2 > 72 ~ 'Stopped as IV beyond 72 hours',
        #                        Route_2 =="Oral" & is.na(Route_3) & Prescription_Length_2 > 72 ~ 'Stopped as Oral beyond 72 hours',
         #                       Route_2 =="Oral" & is.na(Route_3)  ~ 'Stopped as Oral',
          #                      Route_2 == Route_3 & Name_2 == Name_3 & Dose_2 == Dose_3 & Frequency_2 == Frequency_3  ~ 'No Change',
           #                     Route_2 == Route_3 & Name_2 != Name_3  ~ 'Agent changed',
            #                    Decision_1 == "Finalised as Oral" | Decision_1 == "Finalised as IV"  ~ (""),
             #                   Route_2 == Route_3 & Dose_2 != Dose_3 | Frequency_2 != Frequency_3 ~ ('Regiment changed'),
              #                  TRUE ~ 'something else'
  #))

```

```{r Decision 3}

abx_per_indication <- abx_per_indication %>% 
  mutate(Decision_3 = case_when( Route_2 == Route_3 & Name_2 == Name_3 & Dose_2 == Dose_3 & Frequency_2 == Frequency_3  ~ paste0(Route_3, " ", Name_3,  " continued"),    
        Route_2 == Route_3 & Name_2 != Name_3  ~ paste0('Agent switched to ', Name_3),
        Route_2 == Route_3 & Dose_2 != Dose_3 & Frequency_2 != Frequency_3 & Name_2 == Name_3 ~ paste0('Regiment changed to ', Dose_3, " ",Frequency_3),
        Route_2 =="Intravenous" & Route_3 == "Intravenous" & ARK.category_3 == "FINAL" ~ paste0('Finalised as IV ', Name_3),
        Route_2 =="Oral" & Route_3 == "Oral" & is.na(Route_3) & ARK.category_3 == "FINAL" ~ paste0('Finalised as Oral ', Name_3),
        Prescription.end_2 < Prescription.start_3 + 1 ~ paste0(Route_2, " to ", Route_3, " switch"),
        Prescription.end_2 > Prescription.start_3 + 6 ~ paste0(Route_3, " " ,Name_3, " added"),
     is.na(Route_3)  & Prescription_Length_2 <=72 ~ paste0('Stopped as ', Route_2, ' within 72 hours'),
     is.na(Route_3) & Prescription_Length_2 > 72 ~ paste0('Stopped as ', Route_2, ' beyond 72 hours'),
     is.na(Route_2) ~ "",
                                
                                TRUE ~ 'something else'
  ))


temp <- abx_per_indication %>% select(c(Name_1,Route_1,Prescription.start_1, Prescription.end_1, Decision_1, Decision_2, Decision_3, Name_2, Route_2,Name_3,Route_3, Prescription.start_2,Prescription.end_2,interval_1))

```

We will also be able to group people by the number of prescriptions there were in their antibiotic course;

```{r Group by number of prescriptions}

#first get rid of superfluous columns
ark_results <- abx_per_indication %>% 
  select(c(Name_1,Route_1, Name_2,Route_2, Name_3,Route_3,Name_4,Route_4,Decision_1,Decision_2,Prescription_Length_1,Prescription_Length_2,Prescription_Length_3,Prescription_Length_4, Prescription.start_1,Prescription.end_1, Prescription.start_2, Prescription.end_2 , Prescription.start_3)) %>% 
  arrange(Name_4, Name_3, Name_2)

single_rx <- ark_results %>% 
  filter(is.na(Name_2)) %>% 
  select(c(Name_1,Route_1,Decision_1,Decision_2,Prescription_Length_1, Prescription.start_1))

double_rx <- ark_results %>% 
  filter(is.na(Name_3)) %>% 
  select(c(Name_1,Route_1,Prescription_Length_1, Decision_1,Decision_2, Name_2,Route_2,Prescription_Length_2))

triple_rx <- ark_results %>% 
  filter(is.na(Name_4)) %>% 
  select(-c(Name_4,Route_4))

quad_rx <- ark_results %>% 
  filter(!is.na(Name_4))


#pivot long

```



We want to know how long patients' total courses were, so let's do that;

```{a mistake}
#get rid of all missing values, then add course lengths together
course_lengths <-  abx_per_indication 

course_lengths$Prescription_Length_2[is.na(course_lengths$Prescription_Length_2)] <- 0 
course_lengths$Prescription_Length_3[is.na(course_lengths$Prescription_Length_3)] <- 0 
course_lengths$Prescription_Length_4[is.na(course_lengths$Prescription_Length_4)] <- 0 


course_lengths <- course_lengths %>%  mutate( course_length = (Prescription_Length_1 + Prescription_Length_2 + Prescription_Length_3 + Prescription_Length_4))
```

```{r Calculate the total course length}


#make course length the difference in time from the first agent being started and the last agent being finished

course_lengths <- abx_per_indication %>%  mutate(course_length =  case_when(
  is.na(Name_2) ~ Prescription_Length_1,
  is.na(Name_3) ~ interval(Prescription.start_1, Prescription.end_2)/ hours(1),
  is.na(Name_4) ~ interval(Prescription.start_2, Prescription.end_3)/ hours(1),
  is.na(Name_5) ~ interval(Prescription.start_3, Prescription.end_4)/ hours(1),
  is.na(Name_6) ~ interval(Prescription.start_4, Prescription.end_5)/ hours(1),
  is.na(Name_7) ~ interval(Prescription.start_5, Prescription.end_6)/ hours(1),))
 
  
plot_lengths= data.frame(floor(course_lengths$course_length)) %>%  filter(course_lengths$course_length<600)

plot_lengths = plot_lengths %>% group_by(floor.course_lengths.course_length.) %>%  count(floor.course_lengths.course_length.)

plot(plot_lengths
     )

course_lengths <- course_lengths %>%  select(c(course_length, Prescription.start_1,Prescription.start_2,Prescription.start_3,Prescription.start_4))
```

A course counts towards the month that it started in, not the month that it ended in.

ARK also wants to know how many prescriptions were stopped or changed within 72 hours each month, this could be changed to weekly or even hourly if we so desired.

```{r}
#floor all rx dates so they are organised by month. 
#then count the number in each month
rx_in_month <- select(Clean_Data, c(Prescription.start,Prescription_Length))

rx_in_month$Prescription.start <- floor_date(rx_in_month$Prescription.start, "month")

rx_in_month <- rx_in_month %>%  group_by(Prescription.start) %>%  count(Prescription.start)

#do the same as above, but then look for only the rx under 72hrs
rx_under_month <- select(Clean_Data, c(Prescription.start,Prescription_Length))
rx_under_month$Prescription.start <- (floor_date(rx_under_month$Prescription.start, "month")) 
rx_under_month <- rx_under_month %>% mutate(short_rx = Prescription_Length <= 72)
rx_under_month <- rx_under_month %>% 
  filter(short_rx == TRUE) 
rx_under_month <- rx_under_month %>%  group_by(Prescription.start)  %>%  count(short_rx)
#then divide the short rx by total rx
percent_in_month <- data.frame(rx_in_month$Prescription.start) %>%  mutate(percent_short = rx_under_month$n/rx_in_month$n *100)


```

We can then select for people who only had one prescription and whether that was stopped in 72 hours or less; / total course was less than 72 hours

```{r}
stopped_less_72 <- filter(single_rx, Prescription_Length_1 <= 72)

percent_stopped_72 <- nrow(stopped_less_72) / nrow(ark_results) *100
```

Now we want to see the previous result broken down by week

```{r}
rx_under_week_stopped <- select(single_rx, c(Prescription.start_1,Prescription_Length_1,Route_1))
rx_under_week_stopped$Prescription.start_1 <- 
  (floor_date(rx_under_week_stopped$Prescription.start_1, "week")) 
rx_under_week_stopped <- rx_under_week_stopped %>% mutate(short_rx = Prescription_Length_1 <= 72)
rx_under_week_stopped <- rx_under_week_stopped %>% 
  filter(short_rx == TRUE) 
rx_under_week_stopped <- rx_under_week_stopped %>%  group_by(Prescription.start_1)  %>%  count(short_rx)

```

Then we can find the total number of courses each week

```{r}
rx_in_week <- select(Clean_Data, c(Prescription.start,Prescription_Length,Route))

rx_in_week$Prescription.start <- floor_date(rx_in_week$Prescription.start, "week")

rx_in_week <- rx_in_week %>%  group_by(Prescription.start) %>%  count(Prescription.start)
```

Then compare them against each other

```{r}
percent_in_week_stopped <- data.frame(rx_in_week$Prescription.start) %>%  mutate(percent_short = rx_under_week_stopped$n/rx_in_week$n *100)
```

Same as above but only select IV antibiotics

```{r}
rx_under_week_stopped_IV <- select(single_rx, c(Prescription.start_1,Prescription_Length_1,Route_1))
rx_under_week_stopped_IV <- rx_under_week_stopped_IV %>%  filter(Route_1 =="Intravenous" )
rx_under_week_stopped_IV$Prescription.start_1 <- 
  (floor_date(rx_under_week_stopped_IV$Prescription.start_1, "week")) 
rx_under_week_stopped_IV <- rx_under_week_stopped_IV %>% mutate(short_rx = Prescription_Length_1 <= 72)
rx_under_week_stopped_IV <- rx_under_week_stopped_IV %>% 
  filter(short_rx == TRUE) 
rx_under_week_stopped_IV <- rx_under_week_stopped_IV %>%  group_by(Prescription.start_1)  %>%  count(short_rx)

```

Then compare them against each other

```{r}
percent_in_week_stopped_IV <- data.frame(rx_in_week$Prescription.start) %>%  mutate(percent_short = rx_under_week_stopped_IV$n/rx_in_week$n *100)
```

# Data Visualisation

Make a graph of the most common antibiotics used on lilac

```{r}
#top ten prescriptions
  ggplot(data=pop_abx, aes(y=reorder(Name, -n), x = n)) +
    # if wanting abx name on x axis- scale_x_discrete(guide = guide_axis(n.dodge=3)) +
    geom_bar(stat = "identity", fill="Steel Blue", colour="black") +
    xlab("Prescriptions on Lilac | 06-Dec-21 : 07-Mar-21") + ylab("Antibiotic") 

```

Make a graph of the most common indications

```{r}
 ggplot(pop_indic, aes(x =reorder(Reason.given, -n), y = n)) +
    scale_x_discrete("Indication", guide = guide_axis(n.dodge=3), 
    labels = c("Community Acquired Pneumonia" = "CAP",                              "Infective Exacerbation Of Chronic Obstructive Pulmonary Disease" = "IECOPD",
 "Lower Respiratory Tract Infection" = "LRTI",
 "Urinary Tract Infection" = "UTI",
 "Healthcare Associated Pneumonia" = "HAP")) + 
    geom_bar(stat = "identity", fill = "#F066EA")
```

Stacked bar graph of antibiotic for each indication

```{r}

  #stacked bar graph, abx by indic
  Abx_indic_stacked <- agent_by_reason %>%
    filter(Name %in% pop_abx$Name) %>%
    mutate(Reason.given = str_to_title(Reason.given)) %>%
    mutate(Name = str_to_title(Name)) 
  
  Abx_indic_stacked %>% 
    ggplot(aes(x = reorder(Reason.given, -n), y = n, fill =Name)) +
    theme(axis.text.x = element_text(angle = 15, vjust = 0.6)) +
    geom_bar(position='stack', stat='identity') +
    labs(x= "Indication", y= "No of Prescriptions", title="Proportion of Antibiotics by Indication") +
    scale_x_discrete("Indication", labels = c("Community Acquired Pneumonia" = "CAP",
                                              "Infective Exacerbation Of Chronic Obstructive Pulmonary Disease" = "IECOPD",
                                              "Lower Respiratory Tract Infection" = "LRTI",
                                              "Urinary Tract Infection" = "UTI",
                                              "Healthcare Associated Pneumonia" = "HAP"))
  
```

#### ARK Pertinent Graphs

Percent of individual prescriptions that had either stopped or been changed in 72 hours or less by month

```{r}
percent_in_month %>% 
    ggplot(aes(x = rx_in_month.Prescription.start, y = percent_short)) +
    ylim(0,100)+
    labs(x = "Month", y = "Percentage of rx <= 72 hours", title = "Prescriptions Stopped or Changed Within 72 Hours, Lilac Ward Dec '21 - Mar '22") +
    geom_bar(stat = "identity", fill = "coral") 
```

Percent of people who had a total course of less than or equal to 72 hours, by week;

```{r}
percent_in_week_stopped %>% 
    ggplot(aes(x = rx_in_week.Prescription.start, y = percent_short)) +
    ylim(0,100)+
    labs(x = "Month", y = "Percentage of rx <= 72 hours", title = "Antibiotic Courses Stopped Within 72 Hours, Lilac Ward Dec '21 - Mar '22", subtitle = "Including both oral and IV regiments") +
    geom_bar(stat = "identity", colour = "black", fill = "pink")
```

Then look at just IV

```{r IV }
percent_in_week_stopped_IV %>% 
    ggplot(aes(x = rx_in_week.Prescription.start, y = percent_short)) +
    ylim(0,100)+
    labs(x = "Month", y = "Percentage of rx <= 72 hours", title = "Antibiotic Courses Stopped Within 72 Hours, Lilac Ward Dec '21 - Mar '22", subtitle = "IV only") +
    geom_bar(stat = "identity", colour = "black", fill = "pink")
```

Then we can work out the number of people who had their prescription changed to another agent, and what percentage of those people had their first switch in \<=72 hours.

```{r}
#get all courses where the second decision was that the drug was switched
rx_switched <- ark_results %>%  filter(grepl("*switch*", Decision_2, ignore.case = TRUE) | grepl("*change*", Decision_2, ignore.case = TRUE))
#floor by week to group them together
rx_switched$Prescription.start_1 <- floor_date(rx_switched$Prescription.start_1, "week")
#then take those and count how many there were each week
rx_switched_week <- rx_switched %>%  group_by(Prescription.start_1) %>%  count(Prescription.start_1)
#then select only the short ones
rx_switched_short <-rx_switched %>%  filter(Prescription_Length_1 <= 72)
#then count how many there were each week
rx_switched_short_week <- rx_switched_short %>%  group_by(Prescription.start_1) %>%  count(Prescription.start_1)
#then compare them 
percent_in_week_switched <- data.frame(rx_switched_week$Prescription.start_1) %>%  mutate(percent_short = rx_switched_short_week$n/rx_switched_week$n *100)

```

Then put them into a graph!

```{r}
percent_in_week_switched %>% 
    ggplot(aes(x = rx_switched_week.Prescription.start_1, y = percent_short)) +
    ylim(0,100)+
    labs(x = "Month", y = "Percentage of rx <= 72 hours", title = "Proportion of Antibiotic Switches that were Within 72 Hours, Lilac Ward Dec '21 - Mar '22", subtitle = "Including both oral and IV regiments") +
    geom_bar(stat = "identity", colour = "black", fill = "pink")
```

```{r IV to Oral switches done within 72 hours}
#get all courses where the first decision was IV to oral switch
rx_switched <- ark_results %>%  filter(grepl("*Intravenous to Oral*", Decision_2))
#floor by week to group them together
rx_switched$Prescription.start_1 <- floor_date(rx_switched$Prescription.start_1, "week")
#then take those and count how many there were each week
rx_switched_week <- rx_switched %>%  group_by(Prescription.start_1) %>%  count(Prescription.start_1)
#then select only the short ones
rx_switched_short <-rx_switched %>%  filter(Prescription_Length_1 <= 72)
#then count how many there were each week
rx_switched_short_week <- rx_switched_short %>%  group_by(Prescription.start_1) %>%  count(Prescription.start_1)
#then compare them 
percent_in_week_switched <- data.frame(rx_switched_week$Prescription.start_1) %>%  mutate(percent_short = rx_switched_short_week$n/rx_switched_week$n *100)
```

```{r}
percent_in_week_switched %>% 
    ggplot(aes(x = rx_switched_week.Prescription.start_1, y = percent_short)) +
   ylim(0,100)+
    labs(x = "Month", y = "Percentage of rx <= 72 hours", title = "IV to Oral switches that were within 72 Hours of the start of a course | Lilac Ward Dec '21 - Mar '22") +
    geom_bar(stat = "identity", colour = "black", fill = "pink")
```



```{r}
node3e %>% group_by(Reason.given) %>% count() %>% ungroup() %>% top_n(.,5) %>% 
  ggplot(aes(x=reorder(Reason.given,-n), y = n)) +
  geom_bar(stat = "identity") +
  labs(x = "Indication", y = "Prescriptions", title ="Number of courses which were single IV rx, stopped within 72 hrs ")#one rx, less than 72 hrs, IV
node3f %>% group_by(Reason.given) %>% count() %>% ungroup() %>% top_n(.,5) %>% 
  ggplot(aes(x=reorder(Reason.given,-n), y = n)) +
  geom_bar(stat = "identity") +
  labs(x = "Indication", y = "Prescriptions", title ="Number of courses which were single oral rx, stopped within 72 hrs ")  #one rx less than 72 hours oral

node3g %>% group_by(Reason.given) %>% count() %>% ungroup() %>% top_n(.,4) %>%
  ggplot(aes(x=reorder(Reason.given,-n), y = n)) +
  geom_bar(stat = "identity") +
  labs(x = "Indication", y = "Prescriptions", title ="Number of courses which were single IV rx, stopped beyond 72 hrs ")#one rx, less than 72 hrs, IV
node3h %>% group_by(Reason.given) %>% count() %>% ungroup() %>% top_n(.,5) %>% 
  ggplot(aes(x=reorder(Reason.given,-n), y = n)) +
  geom_bar(stat = "identity") +
  labs(x = "Indication", y = "Prescriptions", title ="Number of courses which were single oral rx, stopped beyond 72 hrs ")  #one rx less than 72 hours oral

#bring together the dfs which contain info on single rx courses, one is those which were <72 hrs and one is >72 hrs
#count the instances of long and short rx for each route, select the routes we're interested in
#then group by route and find the % for each category
bind_rows(list(node2b,node2a), .id = "id") %>% 
  group_by(id, Route_1) %>% 
  count() %>% 
  ungroup() %>%  
  filter(Route_1 == "Intravenous" | Route_1 == "Oral") %>%
    group_by(Route_1) %>%  
  mutate(pcnt = n/sum(n)) %>% 
  ungroup() %>% 
  
  ggplot(aes(x = Route_1, 
             y = pcnt, 
             fill = id, 
             label = paste0(round(pcnt*100,2),"%"))) + #then make a stacked bar chart with the groups and &
  geom_col() +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_discrete(name="Prescription\nLength",
                         breaks=c("1","2"),
                         labels=c(">72 Hours","<72 Hours"))+
 geom_text(size = 3, 
           position = position_stack(vjust = 0.5)) +
 labs(title = "Single prescription abx courses by route and course length", 
      x = "", 
      y ="")
#this shows that if a pt receives just one rx, it most likely to stop within 72 hours if it is IV, rather than oral. ?are oral rx being allowed to continue for longer as the prescribers see them as less damaging ?IV rx are being stopped within 72 hours most of the time, which is good ?Does this suggest that most people who are being put on a single IV prescription are being put on them too easily 

```


