---
title: "ARK 72 Hour Review Automation"
author: "Oscar Daniel"
date: '2023-03-28'
output: html_document
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

```{r packages, warning=FALSE}
library(tidyverse)
library(dplyr)
library(lubridate)
library(clock)
library(ggplot2)
library(ggthemes)
library(knitr)
library(readxl)
library(plotly)
options(scipen = 999)

```

# Importing and Cleaning Data

The first thing to do with the data we got from IT is to import it and try to clean it. We need to;

-   Anonymise NHS numbers

-   Make dates correct format

-   Calculate the prescription lengths

-   Remove prescriptions that didn't have at least two administrations

-   Remove duplicates

-   Remove indications that are not antimicrobial.

-   Reformat indications to be consistent and easy to read

```{r import and clean, echo=TRUE}
raw_data <- read_excel("~/R Projects/CQUIN 2/Raw_Data/CQUIN 2 Part 1 (with spell no).xlsx")
raw_data <- raw_data %>% rename(NHS. = PER_NHS_NO, 
                                Prescription.start = `Prescription start`, 
                                Prescription.end = `Prescription end`, 
                                Reason.given = `Reason given`, 
                                ARK.category = `ARK category` )

  #read.csv(file = "RAW_DATA\\Data Extract.csv")
Clean_Data <- raw_data 


PID <- Clean_Data %>%                                        # Create ID by group
  group_by(NHS.) %>%
  mutate(ID = cur_group_id())
Clean_Data$NHS. <- PID$ID



Clean_Data$Prescription.start <- ymd_hms(Clean_Data$Prescription.start)
Clean_Data$Prescription.end <- ymd_hms(Clean_Data$Prescription.end)

Clean_Data$Reason.given <-str_to_upper(Clean_Data$Reason.given, locale ="en") 
Clean_Data$Name <-str_to_title(Clean_Data$Name, locale ="en")
Clean_Data$Route <-str_to_title(Clean_Data$Route, locale ="en")
Clean_Data <- Clean_Data %>%  filter(!is.na(Reason.given))

Clean_Data$Prescription_Length <- interval(Clean_Data$Prescription.start, Clean_Data$Prescription.end) / hours(1)

 Clean_Data <- filter(Clean_Data, Frequency == "THREE times a DAY" & Prescription_Length > 8 | 
                        Frequency == "FOUR times a DAY" & Clean_Data$Prescription_Length > 6 | 
                        Frequency == "TWICE a DAY" & Prescription_Length > 12)

 Clean_Data <- Clean_Data %>%
              group_by(NHS., 
                       SPELL_NUMBER,
                       ORG_NAME,
                      Prescription.start,
                      Prescription.end,
                       Name,
                       Dose,
                       Frequency,
                       Route,
                      Reason.given,
                      ARK.category) %>% slice(1) %>% ungroup()
 
Clean_Data <- Clean_Data[!duplicated(Clean_Data), ]

Clean_Data <- filter(Clean_Data, Prescription.start >= as.POSIXct("2021-12-01 00:00"))

Clean_Data <- filter(Clean_Data, Prescription.end < as.POSIXct("2022-12-31 00:00"))

 Clean_Data <- Clean_Data %>%
    filter(!(grepl("*BLEED*", Reason.given) | grepl("*PROPHY*", Reason.given) | grepl("*CRAMP*", Reason.given) | 
               grepl("MS", Reason.given) | grepl("*ONCE*", Frequency) | grepl("H.ENCEPH*", Reason.given) | grepl("*HEPATIC ENCEPHALOPATHY*", Reason.given) | grepl("NYSTATIN", Name) | grepl("NYSTATIN", Name) | grepl("SIADH", Reason.given) | grepl("^Amantadine", Name)))
 
 
 #make all UTIs display as Urinary Tract Infection
  Clean_Data$Reason.given <- gsub( "UTI", "URINARY TRACT INFECTION",Clean_Data$Reason.given) 
  
  #make all community acquired pneumonia display as CAP
  Clean_Data$Reason.given <- gsub("CAP", "COMMUNITY ACQUIRED PNEUMONIA", Clean_Data$Reason.given)
  
  #make all IEoCOPD as IECOPD
  Clean_Data$Reason.given <- gsub("IECOPD", "INFECTIVE EXACERBATION OF CHRONIC OBSTRUCTIVE PULMONARY DISEASE", Clean_Data$Reason.given) 
  
  #make all LRTI full name
  Clean_Data$Reason.given <- gsub("LRTI", "LOWER RESPIRATORY TRACT INFECTION", Clean_Data$Reason.given) 
  #make any blank indications "Unrecorded"
  Clean_Data$Reason.given <- sub("^$", "UNRECORDED", Clean_Data$Reason.given)
  
  #correct common spelling mistakes
  Clean_Data$Reason.given <- gsub("PYONEPHRITIS", "PYELONEPHRITIS", Clean_Data$Reason.given)
  
  Clean_Data$Reason.given <- replace(Clean_Data$Reason.given,grep("DIFF",Clean_Data$Reason.given),"CLOSTRIDIUM DIFFICILE")
    
  
  Clean_Data$Reason.given <- str_to_title(Clean_Data$Reason.given)


```

# Data Manipulation

Now we need to change the data so that it gives us what we want. We want to see antibiotic courses, not individual prescriptions. We do this by grouping prescriptions by NHS, spell number and indication.

```{r pivoting, echo=TRUE}

#pivot wide
abx_per_indication <- Clean_Data %>% arrange(Prescription.start) %>% #group_by(NHS.)
  group_by(NHS.,SPELL_NUMBER, Reason.given) %>% 
  mutate(rn = row_number()) %>%
  pivot_wider(values_from = c(Name,Route,Prescription.start,Prescription.end, Dose, 
                              Frequency, ARK.category, Prescription_Length, WARD, ORG_NAME ),
              names_from =  rn)
```

Then we select courses where the ARK indication of the first prescription was not final and only take the information about the first prescription.

```{r, echo=TRUE}

first_rx <- abx_per_indication %>% 
  filter(ARK.category_1 != "FINAL") %>% 
  select(SPELL_NUMBER,NHS.,Reason.given,Name_1,Route_1,Frequency_1,Dose_1,ORG_NAME_1,WARD_1,Prescription.start_1,Prescription.end_1,Prescription_Length_1, ARK.category_1)

```

Then we can look at what proportion of these prescriptions were reviewed within 72 hours.

```{r, warning=FALSE, echo=TRUE}

# Calculate the percentage of rows with Prescription_Length <= 72
percent_short_prescriptions <- round((sum(first_rx$Prescription_Length_1 <= 72) / nrow(first_rx)) * 100, digits=1)

# Print the result
cat("Percentage of rows with ARK.category != \"FINAL\" and Prescription_Length <= 72:", percent_short_prescriptions, "%\n")

monthly_data_ward <- first_rx %>%
  mutate(month = format(Prescription.start_1, "%Y-%m")) %>%
  group_by(WARD_1, month) %>%
  summarise(n_short_prescriptions = sum(ARK.category_1 != "FINAL" & Prescription_Length_1 <= 72),
            n_total_prescriptions = n()) %>%
  ungroup() %>%
  mutate(percent_short_prescriptions = n_short_prescriptions / n_total_prescriptions * 100)


monthly_data_org <- first_rx %>%
  mutate(month = format(Prescription.start_1, "%Y-%m")) %>%
  group_by(ORG_NAME_1, month) %>%
  summarise(n_short_prescriptions = sum(ARK.category_1 != "FINAL" & Prescription_Length_1 <= 72),
            n_total_prescriptions = n()) %>%
  ungroup() %>%
  mutate(percent_short_prescriptions = n_short_prescriptions / n_total_prescriptions * 100)



line_graph_ward <- monthly_data_ward %>%
  plot_ly(.,x = ~month, y = ~percent_short_prescriptions, color = ~WARD_1, type = 'scatter', mode = 'lines+markers',
          line = list(shape = 'spline', smoothing = 1.3)) %>%
  layout(title = "Monthly Percentages of Short Antibiotic Prescriptions by Ward",
         xaxis = list(title = "Month"),
         yaxis = list(title = "Percentage of Short Antibiotic Prescriptions"))


line_graph_org <- monthly_data_org %>%
  plot_ly(.,x = ~month, y = ~percent_short_prescriptions, color = ~ORG_NAME_1, type = 'scatter', mode = 'lines+markers',
          line = list(shape = 'spline', smoothing = 1.3)) %>%
  layout(title = "Monthly Percentages of Short Antibiotic Prescriptions by Organisation",
         xaxis = list(title = "Month"),
         yaxis = list(title = "Percentage of Short Antibiotic Prescriptions"))



# Print the line graph
line_graph_ward
line_graph_org

# Create a line graph of the monthly percentages using ggplot2
plot_2 <- ggplot(monthly_data_ward, aes(x = month, y = percent_short_prescriptions, color = WARD_1)) +
  geom_line(size = 1.5, aes(group = WARD_1), alpha = 0.8) +
  geom_point(size = 3, alpha = 0.8) +
  theme_minimal() +
  labs(title = "Monthly Percentages of Short Antibiotic Prescriptions by WARD_1",
       x = "Month",
       y = "Percentage of Short Antibiotic Prescriptions")

#ggplotly(plot_2)

bar_graph_ward <- monthly_data_ward %>%
  plot_ly(x = ~month, y = ~percent_short_prescriptions, color = ~WARD_1, type = 'bar') %>%
  layout(title = "Monthly Percentages of Short Antibiotic Prescriptions by WARD_1",
         xaxis = list(title = "Month"),
         yaxis = list(title = "Percentage of Short Antibiotic Prescriptions"))
bar_graph_ward

bar_graph_ward <- monthly_data_ward %>%
  plot_ly(x = ~month, y = ~percent_short_prescriptions, color = ~WARD_1, type = 'bar') %>%
  layout(title = "Monthly Percentages of Short Antibiotic Prescriptions by WARD_1",
         xaxis = list(title = "Month"),
         yaxis = list(title = "Percentage of Short Antibiotic Prescriptions"))


bar_graph_org <- monthly_data_org %>%
  plot_ly(x = ~month, y = ~percent_short_prescriptions, color = ~ORG_NAME_1, type = 'bar') %>%
  layout(title = "Monthly Percentages of Short Antibiotic Prescriptions by Organisation",
         xaxis = list(title = "Month"),
         yaxis = list(title = "Percentage of Short Antibiotic Prescriptions"))
bar_graph_org

#histogram of prescription lengths


plot_ly(data = first_rx, x = ~Prescription_Length_1) %>% 
  add_histogram(xbins = list(start = 0, end = 240, size = 24), 
                marker = list(color = "green")) %>% 
  layout(title = "Prescription Length Distribution",
         xaxis = list(title = "Prescription Length (hours)"),
         yaxis = list(title = "Frequency"))

#top five indications 

top5_reasons <- first_rx %>% 
  ungroup() %>% 
  count(Reason.given) %>% 
  top_n(5, n) %>% 
  select(Reason.given)

plot_data <- first_rx %>% ungroup() %>% 
  filter(Reason.given %in% top5_reasons$Reason.given) %>% 
  count(Reason.given) %>% 
  arrange(desc(n))

plot_ly(data = plot_data, x = ~Reason.given, y = ~n, type = "bar", 
        marker = list()) %>% 
  layout(title = "Top 5 Reasons Given for Prescription",
         
         xaxis = list(title = "Reason Given", 
                      categoryorder = "array", 
                      categoryarray = plot_data$Reason.given[order(plot_data$n, decreasing = TRUE)]),
         yaxis = list(title = "No. of Prescriptions"))

```

```{r}
#bar graph showing % of rx under 72 hours by indication
cutoff_length <- 72

top5_reasons <- first_rx %>% ungroup() %>% 
  count(Reason.given) %>% 
  top_n(5, n) %>% 
  select(Reason.given)

plot_data <- first_rx %>% 
  filter(Reason.given %in% top5_reasons$Reason.given) %>% 
  group_by(Reason.given) %>% 
  summarize(total_prescriptions = n(),
            short_prescriptions = sum(Prescription_Length_1 <= cutoff_length)) %>% 
  ungroup() %>% 
  mutate(short_pct = short_prescriptions/total_prescriptions * 100,
         long_pct = 100 - short_pct)

plot_ly(data = plot_data, x = ~Reason.given, type = "bar", 
        name = "<=72 hours", y = ~short_pct) %>% 
  add_trace(y = ~long_pct, name = ">72 hours") %>% 
  layout(title = "Top 5 Reasons Given for Prescription",
         legend = list(title = list(text="Prescription Length")),
         xaxis = list(title = "Reason Given"), 
         yaxis = list(title = "% of Prescriptions")) %>% 
  layout(barmode = "stack")

```

A table showing the wards with the lowest % of reviews each month.

```{r}

#worst ward by month


lowest_ward <- monthly_data_ward %>%
  group_by(month) %>%
  filter(percent_short_prescriptions == min(percent_short_prescriptions)) %>%
  select(month, WARD_1, percent_short_prescriptions)

kable(lowest_ward)

```

```{r}

avg_prescription_length <- Clean_Data %>%
  group_by(Name) %>%
  summarize(Avg_Prescription_Length = mean(Prescription_Length))

# Create a bar chart of the average prescription length by medication
ggplot(data = avg_prescription_length, aes(x = reorder(Name, -Avg_Prescription_Length), y = Avg_Prescription_Length)) +
  geom_bar(stat = "identity", fill = "blue") +
  labs(title = "Average Prescription Length by Medication", x = "Medication", y = "Average Prescription Length (Hours)") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

ggplot(data = avg_prescription_length, aes(x = reorder(Name, -Avg_Prescription_Length), y = Avg_Prescription_Length/24)) +
  geom_bar(stat = "identity", fill = "red") +
  labs(title = "Average Prescription Length by Medication", x = "Medication", y = "Average Prescription Length (Days)") +
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

# Create a histogram of the distribution of prescription lengths

# Histogram of prescription lengths
ggplot(data = Clean_Data, aes(x = Prescription_Length)) +
  geom_histogram(binwidth = 24, fill = "steelblue", color = "white") +
  labs(title = "Distribution of Prescription Lengths",
       x = "Prescription Length (hours)",
       y = "Count") +
  theme_minimal() +
  theme(plot.title = element_text(size = 20, face = "bold", hjust = 0.5),
        axis.title = element_text(size = 14),
        axis.text = element_text(size = 12),
        panel.grid.major = element_line(colour = "gray80", linetype = "dashed")) +
  scale_x_continuous(limits = c(0, max(Clean_Data$Prescription_Length)))
  
```

```{r}

# Create a subset of the data to calculate prescription length percentage
sub_data <- first_rx %>%
  filter(Prescription_Length_1 <= 72) %>%
  group_by(ORG_NAME_1, WARD_1) %>%
  summarize(pct_prescription_length = n()/nrow(first_rx) * 100)

# Create the plot
plot <- plot_ly(sub_data, x = ~ORG_NAME_1, y = ~WARD_1, size = ~pct_prescription_length, 
                color = ~pct_prescription_length, colors = "Blues") %>%
  add_markers()

# Add axis labels and title
plot <- plot %>% layout(xaxis = list(title = "Organisation Name"), 
                        yaxis = list(title = "Ward"), 
                        title = "Percentage of Prescriptions with Length <= 72 hours")
                        
# Show the plot
plot


sub_data <- first_rx %>%
  filter(Prescription_Length_1 <= 72) %>%
  group_by(ORG_NAME_1, WARD_1) %>%
  summarize(pct_prescription_length = n()/nrow(first_rx) * 100)

# Create the plot
plot <- plot_ly(sub_data, x = ~ORG_NAME_1, y = ~WARD_1, size = ~pct_prescription_length, 
                color = ~pct_prescription_length, colors = "Blues") %>%
  add_markers()

# Add axis labels and title
plot <- plot %>%layout(yaxis = list(showticklabels = FALSE), 
         xaxis = list(title = "Organization Name"), 
         margin = list(l = 150, r = 20, b = 50, t = 50, pad = 4))
                        
# Show the plot
plot


```

```{r heatmap}
library(plotly)
library(dplyr)
library(lubridate)

# Create a month column in the original dataset
first_rx <- first_rx %>% mutate(month = floor_date(Prescription.start_1, unit = "month"))

# Group the data by month and ward, and calculate the percentage of prescriptions that were less than or equal to 72 hours for each ward within each month
pct_short_prescriptions <- first_rx %>% 
  group_by(month, WARD_1) %>%
  summarise(total_prescriptions = n(),
            short_prescriptions = sum(Prescription_Length_1 <= 72)) %>%
  mutate(pct_short = short_prescriptions / total_prescriptions * 100)

# Create the heatmap
plot_ly(data = pct_short_prescriptions, x = ~month, y = ~WARD_1, z = ~pct_short, type = "heatmap") %>%
  layout(title = "Monthly average percentage of prescriptions that were <=72 hours by ward",
         xaxis = list(title = "Month"),
         yaxis = list(title = "Ward"),
         coloraxis = list(colorscale = "reds"),
         width = 800,
         height = 600)

```

```{r}
# Create the monthly data by organization
monthly_data_org <- first_rx %>%
  mutate(month = format(Prescription.start_1, "%Y-%m")) %>%
  group_by(ORG_NAME_1, month) %>%
  summarise(n_short_prescriptions = sum(ARK.category_1 != "FINAL" & Prescription_Length_1 <= 72),
            n_total_prescriptions = n()) %>%
  ungroup() %>%
  mutate(percent_short_prescriptions = n_short_prescriptions / n_total_prescriptions * 100)

# Create the heatmap
heatmap_org <- monthly_data_org %>%
  ggplot(aes(x = month, y = ORG_NAME_1, fill = percent_short_prescriptions)) +
  geom_tile() +
  scale_fill_gradient(low = "white", high = "red") +
  labs(title = "Percentage of Short Antibiotic Prescriptions by Organization and Month",
       x = "Month",
       y = "Organization Name",
       fill = "Percentage of Short Antibiotic Prescriptions") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 90))

# Print the heatmap
heatmap_org

```

```{r}
# Create a line graph of the monthly percentages by organisation using ggplot2
plot_3 <- ggplot(monthly_data_org, aes(x = month, y = percent_short_prescriptions, color = ORG_NAME_1)) +
  geom_line(size = 1.5, aes(group = ORG_NAME_1), alpha = 0.8) +
  scale_y_continuous(sec.axis = sec_axis(~./max(monthly_data_org$percent_short_prescriptions)*100, name = "Percentage of Short Antibiotic Prescriptions"), name = "Percentage of Short Antibiotic Prescriptions") +
  theme_minimal() +
  labs(title = "Monthly Percentages of Short Antibiotic Prescriptions by Organisation",
       x = "Month",
       y = "Percentage of Short Antibiotic Prescriptions")

# Split the plot into facets
plot_3 <- plot_3 + facet_wrap(~ ORG_NAME_1, scales = "free_y", ncol = 2)

# Print the line graph
plot_3


# Set colors for the lines
colors <- c("#1f77b4", "#ff7f0e", "#2ca02c", "#d62728", "#9467bd", "#8c564b", "#e377c2", "#7f7f7f", "#bcbd22", "#17becf")

# Create a list to store the individual graphs
graphs <- list()

# Loop over each organization to create a line graph for each one
for (i in 1:length(unique(monthly_data_org$ORG_NAME_1))) {
  # Subset the data for the current organization
  current_data <- monthly_data_org %>% filter(ORG_NAME_1 == unique(monthly_data_org$ORG_NAME_1)[i])
  
  # Create a new plotly line graph
  current_graph <- plot_ly(current_data, x = ~month, y = ~percent_short_prescriptions, type = 'scatter', mode = 'lines+markers',
                           line = list(color = colors[i], shape = 'spline', smoothing = 1.3),
                           name = unique(monthly_data_org$ORG_NAME_1)[i], hovertemplate = paste('%{x}<br>', '%{y:.1f}%<br>')) %>%
    layout(yaxis = list(title = "Percentage of Short Antibiotic Prescriptions", 
                         range = c(min(monthly_data_org$percent_short_prescriptions), max(monthly_data_org$percent_short_prescriptions))),
           xaxis = list(title = "Month"),
           title = "Monthly Percentages of Short Antibiotic Prescriptions by Organization")
  
  # Add the current graph to the list of graphs
  graphs[[i]] <- current_graph
}

# Combine the individual graphs into a single plotly object
combined_graph <- subplot(graphs, nrows = length(unique(monthly_data_org$ORG_NAME_1)), shareX = TRUE, titleX = FALSE, titleY = FALSE) %>%
  layout(yaxis = list(title = "Percentage of Short Antibiotic Prescriptions"))

# Print the combined graph
combined_graph

```

```{r weekly graphs}

# Summarize by week
weekly_data_org <- first_rx %>%
  mutate(week = format(Prescription.start_1, "%Y-%W")) %>%
  group_by(ORG_NAME_1, week) %>%
  summarise(n_short_prescriptions = sum(ARK.category_1 != "FINAL" & Prescription_Length_1 <= 72),
            n_total_prescriptions = n()) %>%
  ungroup() %>%
  mutate(percent_short_prescriptions = n_short_prescriptions / n_total_prescriptions * 100)

weekly_data_ward <- first_rx %>%
  mutate(week = format(Prescription.start_1, "%Y-%W")) %>%
  group_by(WARD_1, week) %>%
  summarise(n_short_prescriptions = sum(ARK.category_1 != "FINAL" & Prescription_Length_1 <= 72),
            n_total_prescriptions = n()) %>%
  ungroup() %>%
  mutate(percent_short_prescriptions = n_short_prescriptions / n_total_prescriptions * 100)


# Create a heatmap of the weekly percentages
heatmap_weekly_org <- weekly_data_org %>%
  ggplot(aes(x = week, y = ORG_NAME_1, fill = percent_short_prescriptions)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "white", high = "blue", na.value = "white", name = "Percentage of Short Prescriptions") +
  theme_minimal() +
  ggtitle("Weekly Percentages of Short Antibiotic Prescriptions by Organisation") +
  labs(x = "Week", y = "Organisation")

# Create a heatmap of the weekly percentages
heatmap_weekly_ward <- weekly_data_ward %>%
  ggplot(aes(x = week, y = WARD_1, fill = percent_short_prescriptions)) +
  geom_tile(color = "white") +
  scale_fill_gradient(low = "white", high = "blue", na.value = "white", name = "Percentage of Short Prescriptions") +
  theme_minimal() +
  ggtitle("Weekly Percentages of Short Antibiotic Prescriptions by Ward") +
  labs(x = "Week", y = "Ward")


# Create a line graph of the weekly percentages by organisation
line_graph_weekly_org <- weekly_data_org %>%
  ggplot(aes(x = week, y = percent_short_prescriptions, color = ORG_NAME_1, group = ORG_NAME_1)) +
  geom_line(size = 1.5, alpha = 0.8) +
  geom_point(size = 3, alpha = 0.8) +
  theme_minimal() +
  labs(title = "Weekly Percentages of Short Antibiotic Prescriptions by Organisation",
       x = "Week",
       y = "Percentage of Short Antibiotic Prescriptions") +
  facet_wrap(~ORG_NAME_1, scales = "free_y")

# Create a line graph of the weekly percentages by ward
line_graph_weekly_ward <- weekly_data_ward %>%
  ggplot(aes(x = week, y = percent_short_prescriptions, color = WARD_1, group = WARD_1)) +
  geom_line(size = 1.5, alpha = 0.8) +
  geom_point(size = 3, alpha = 0.8) +
  theme_minimal() +
  labs(title = "Weekly Percentages of Short Antibiotic Prescriptions by Ward",
       x = "Week",
       y = "Percentage of Short Antibiotic Prescriptions") +
  facet_wrap(~WARD_1, scales = "free_y")

```
